Fixed-Shape Ellipse by Three Points

### 2019-10-17 ONPCE/slides.tex
wip

	Let's rotate the points instead of rotating the ellipse. A solution can be transformed into the original problem.

@@

\begin{frame}{Transforming the problem}
	Transforming it into a circle problem.

	\begin{itemize}
		\item Translate the points so $u=(0, 0)$.
		\item The ellipse is fixed, the points rotate.
		\item Scale the $x$-axis by $\frac{b}{a}$.
	\end{itemize}

	After the transformation, the points are defined by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:

	\begin{equation*}\label{eq:trpnts}
	\varphi(p, \theta)=\left[\begin{array}{cc}
	\frac{b}{a}&0\\
	0&1
	\end{array}\right]
	\left[\begin{array}{cc}
	\cos{\theta}&\sin{\theta}\\
	-\sin{\theta}&\cos{\theta}
	\end{array}\right]\left[\begin{array}{c}
	p_x\\
	p_y
	\end{array}\right].
	\end{equation*}
\end{frame}

\begin{frame}{Transforming the problem}
	Find every $\theta \in [0, \pi)$, such that:

	\begin{itemize}
		\item The circumscribe circle determined by: $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.

		\item As long as they are not colinear, there is an unique circumscribe circle by three points.

@@

>>>>

	Let's rotate the points instead of rotating the ellipse. It is equivalent:

@@

\begin{frame}{Transforming the problem}
	Formally, we can transform the problem by:

	\begin{itemize}
		\item Translate the points so $u=(0, 0)$.
		\item Scale the $x$-axis by $\frac{b}{a}$.
	\end{itemize}

	Then, we rotate the points. The rotated points are $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$:

	\begin{equation*}\label{eq:trpnts}
	\varphi(p, \theta)=\left[\begin{array}{cc}
	\frac{b}{a}&0\\
	0&1
	\end{array}\right]
	\left[\begin{array}{cc}
	\cos{\theta}&\sin{\theta}\\
	-\sin{\theta}&\cos{\theta}
	\end{array}\right]\left[\begin{array}{c}
	p_x\\
	p_y
	\end{array}\right].
	\end{equation*}

	After that, we need to look at the circumscribed circle formed by $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.
\end{frame}

	\textbf{An angle is a solution if, and only if the circumscribed circle of the points  $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ has radius $b$.}

	\begin{itemize}
		\item This is a problem of one variable!

@@

\begin{frame}{Fixed-shape ellipse by three points}
	There is no clear pattern in $\xi$.
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.5]{035}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with two roots.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{012}
		\caption{Another example of $\xi$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}
